\documentclass{resume} 

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\usepackage[inline]{enumitem}
\usepackage{multicol}
\usepackage{textcomp}
\usepackage{graphicx,xcolor,fontawesome}
\usepackage{hanging}
\usepackage[colorlinks=true,urlcolor=black]{hyperref}


\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\newcommand{\subhead}[1]{{\bf #1 \vspace{2ex}\\}}
\newlength{\hangwidth}
\newcommand{\newhang}[1]{\settowidth{\hangwidth}{#1}\par\hangpara{\hangwidth}{1}#1}
\definecolor{black}{RGB}{0, 0, 0}
\newcommand{\seticon}[1]{\textcolor{black}{\csname #1\endcsname}}
\name{Kyle Posluns}

\availability{Available: January - June 2020}

\address{
\seticon{faMobile} (224) 944-7221 
\\ \href{mailto:posluns.k@husky.neu.edu}{\seticon{faEnvelope} posluns.k@husky.neu.edu}
\\ \href{http://www.kyleposluns.com}{\seticon{faHome} kyleposluns.com}
\\ \href{https://www.github.com/kyleposluns}{\seticon{faGithubSquare} kyleposluns}
\\ \href{https://www.linkedin.com/in/kyleposluns}{\seticon{faLinkedin} kyleposluns}}

\begin{document}
\begin{rSection}{Education}
\begin{rSubsection}{Northeastern University\normalfont {, Boston, MA}}{September 2018 - Present}{Khoury College of Computer Sciences}{\normalfont{GPA: 3.61/4.00}}
\item Expected Graduation Date: 2023.
\item Relevant Courses: Object-Oriented Design, Computer Systems, Algorithms and Data, Foundations of Cyber Security, Database Design, Discrete Structures, Mathematics of Data Models.
\item Awards: Dean's List, 2018 - Present.
\end{rSubsection}

{\bf Grayslake North High School}, Grayslake, IL \hfill {August 2014 - June 2018}

\end{rSection}

\begin{rSection}{Skills}
  \begin{list}{\tiny\raisebox{1ex}{\textbullet}}{\leftmargin=2.0em}
    \item Languages: Java, Python, Racket (BSL/ISL), SQL, HTML/CSS, C, Bash, x86 assembler. 
    \item Tools: JetBrains suite, Git, Maven, Gradle, MongoDB, Latex.
    \item Operating Systems: macOS, Linux/Unix, Windows (7 $\to$ 10).
    \item Frameworks/Libraries: Selenium, Flask, spaCy.
  \end{list}
\end{rSection}
\begin{rSection}{Projects}

\begin{rSubsection}{\href{https://www.devpost.com/software/CrimePot}{{\bf CrimePot: (HackBeanpot 2019)}}}{February 2019}{}{}
\item Integrated Boston Police data into an accessible user interface built on Google Maps.
\item Designed to inspire change in disadvantaged areas by indicating places that might need additional resources to combat crime.
\end{rSubsection}

\begin{rSubsection}{\href{https://www.devpost.com/software/SpeechShifter}{\bf Speech Shifter: (HackMIT 2019)}}{September 2019}{}{}
\item Adjusted speed of YouTube videos depending on language difficulty of each spoken sentence.
\item Utilized \href{https://www.spacy.io}{"spaCy"} Natural Language Processing to tokenize YouTube-generated subtitles into sentences.
\item Determined difficulty of sentences using Flesch reading-ease score (FRES) test.
\end{rSubsection}

\end{rSection}

\begin{rSection}{Work Experience}

\begin{rSubsection}{Tech Team}{April 2019 - Present}{HackBeanpot}{Boston, MA}
\item Collaborated with a diverse team to organize a hackathon focused on participant growth.
\end{rSubsection}

\begin{rSubsection}{Research Assistant}{July 2019 - Present}{Mon(IOT)r Research Group at Northeastern University}{Boston, MA}
\item Reverse-Engineered Amazon's internal Alexa API using a man-in-the-middle (mitm) proxy. 
\item Built a script that scrapes Amazon's website for audio recordings generated by Amazon Alexa.
\end{rSubsection}

\begin{rSubsection}{Sales Consultant}{July 2017 - July 2019}{Best Buy}{Gurnee, IL}
\item Promoted an educational sales style, recognized for excellence in customer service, and responsible for building relationships with customers and their technology.
\end{rSubsection}

\end{rSection}

\begin{rSection}{Extracurricular}\itemsep -5pt
{\bf Activities:}
Publicity Chair of NU Hacks, Husky Ambassador, Intramural Volleyball. \\
{\bf Interests:}
Connecting people to technology, IOT Devices, Raspberry Pi, Baseball, Improvisation.
\end{rSection}


\end{document}

 \\  \smallskip \\\smallskip \smallskip \\